\mythesistitle

### 2011-11-21 src/synopsis.tex
- formatted the COP example figure. have text instead of the png from doms.

The interval assignment problem to a set system is equivalent to the
consecutive ones problem (COP) in binary matrices\cite{wlh02,
  nsnrs09}.  The COP problem is to rearrange rows (columns) of a
binary matrix in such a way that every column (row) has its $1$s occur
consecutively. If this is possible the matrix is said to have the COP.
Consecutive ones property (COP) of binary matrices is a well
researched combinatorial problem and has several positive results on
tests for it and computing the COP permutation (i.e. the class slot
allocation to course IDs in the above illustration) which will be
surveyed later in this document. Hence we are interested in extensions
of COP, more specifically, the extension of interval assignment
problem to tree path assignment problem (which is illustrated by the
study group accommodation problem).

@@

Section~\ref{sec:motivation} gives a brief survey of COP and relatives.
Section~\ref{sec:results} presents a summary of our results on the
tree path labeling problem.

@@

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[scale=0.4]{../img/0_cop_nocop.png}

  \caption{{\em Example for the COP:} The matrix on the left has the
    COP because by permuting its columns (labeled with $c_1$-$c_4$)
    one can obtain the matrix shown in the middle where the 1s in each
    row appear consecutively. The matrix on the right, in contrast,
    does not have the COP \cite{at72,d08phd}.}
  \label{fig:cop-matrix}
\end{figure}

>>>>

The interval assignment problem to a set system is equivalent to the
consecutive ones problem (COP) in binary matrices\cite{wlh02,
  nsnrs09}.  The COP problem is to rearrange rows (columns) of a
binary matrix in such a way that every column (row) has its $1$s occur
consecutively. If this is possible the matrix is said to have the COP.
Consecutive ones property (COP) of binary matrices is a well
researched combinatorial problem and has several positive results on
tests for it and computing the COP permutation (i.e. the course
schedule in the above illustration) which will be surveyed later in
this document. Hence we are interested in extensions of COP, more
specifically, the extension of interval assignment problem to tree
path assignment problem (which is illustrated by the study group
accommodation problem).

@@

Section~\ref{sec:motivation} gives a brief survey of COP and
optimization problems related to it.  Section~\ref{sec:results}
presents a summary of our results on the extention of COP namely, the
tree path labeling problem.

@@

%The course scheduling problem illustated earlier, as a special case of

It is quite obvious now why this version of the
problem (where the ``target graph'' is a path and not any
tree\tnote[TH]{Allowing any tree in this example could be seen as a
  scenario where there are parallel classes. A node falling in the
  path between two other nodes would mean that the corresponding is
  scheduled between the other two.}) is called an interval assignment
problem.

The interval assignment problem to a set system is equivalent to the
consecutive ones problem (COP) in binary matrices\cite{wlh02,
  nsnrs09}.  The COP problem is to rearrange rows (columns) of a
binary matrix in such a way that every column (row) has its $1$s occur
consecutively. If this is possible the matrix is said to have the COP.
Consecutive ones property (COP) of binary matrices is a well
researched combinatorial problem and has several positive results on
tests for it and computing the COP permutation (i.e. the course
schedule in the above illustration) which will be surveyed later in
this document. Hence we are interested in extensions of COP, more
specifically, the extension of interval assignment problem to tree
path assignment problem (which is illustrated by the study group
accommodation problem).

@@

\def \un {\bf 1}
\begin{figure}[htbp]
  \centering
  % \includegraphics[scale=0.4]{../img/0_cop_nocop.png}
  \begin{tabular}[h]{l|lcccl}
    $M_1$: & $M_1'$: &&&& $M_2$:\\
    &&&&&\\
    \begin{tabular}[h]{llll}
      $c_1$ & $c_2$ &$c_3$ &$c_4$\\
      &&&\\
      \un & 0   & \un & 0\\
      0   & \un & 0   & \un \\
      \un & 0   & 0   & \un
    \end{tabular}
    &
    \begin{tabular}[h]{llll}
      $c_3$ &$c_1$ &$c_4$& $c_2$\\
      &&&\\
      \un & \un & 0 & 0\\
      0 & 0 & \un & \un \\
      0 & \un & \un & 0
    \end{tabular}
    &&&&
    \begin{tabular}[h]{llll}
      $d_1$ & $d_2$ &$d_3$ &$d_4$\\
      % &&&\\
      &&&\\
      \un & \un & 0 & 0\\
      0 & \un & \un & 0 \\
      0 & \un & 0 & \un 
    \end{tabular}
  \end{tabular}
  \caption{Matrices with and without COP. $M_1$ has COP because by
    permuting its columns, $c_1$-$c_4$, one can obtain $M_1'$ where
    the {\un}s in each row are consecutive. $M_2$, however, does not
    have COP since no permutation of its columns, $d_1$-$d_4$, will
    arrange {\un}s in each row consecutively \cite{d08phd}.}
  \label{fig:cop-matrix}
\end{figure}
